
\begin{appendices}


\newcolumntype{P}{>{\centering\arraybackslash}p{0.75cm}}
\newcolumntype{L}{>{\raggedright\arraybackslash}m{0.2\textwidth}}
\newcolumntype{R}{>{\raggedleft\arraybackslash}m{0.2\textwidth}}

\newcommand{\printtblhdr}{%
  \hfill
  \begingroup
  \setlength\tabcolsep{0pt}%
  \begin{tabularx}{0.41\textwidth}{ @{} l *{3}X r @{} }
    \multicolumn{2}{l}{\bfseries\shortstack[l]{Strongly\\ Disagree}}
    &&
    \multicolumn{2}{l}{\bfseries\shortstack[r]{Strongly\\ Agree}}
    \\
  \end{tabularx}
  \endgroup
}

\newcommand{\usetbl}{%
  \begin{tabular}{@{}|*5{P|}@{}}
    \hline
    1 & 2 & 3 & 4 & 5 \\
    \hline
  \end{tabular}
}

\newcommand\prop[1]{%
  \item
  \parbox[t]{0.5\textwidth}{#1}%
  \qquad
  \parbox[t]{0.5\textwidth}{\usetbl}%
}






\chapter{System Usability Scale Table} \label{appendix:sus}

\printtblhdr

\begin{enumerate}
\prop{I think that I would like to use this system frequently}

\prop{I found the system unnecessarily complex}

\prop{I thought the system was easy to use}

\prop{I think that I would need the support of a technical person to be able to use this system}

\prop{I found the various functions in this system were well integrated}

\prop{I thought there was too much inconsistency in this system}

\prop{I would imagine that most people would learn to use this system very quickly}

\prop{I found the system very cumbersome to use}

\prop{I felt very confident using the system}

\prop{I needed to learn a lot of things before I could get going with this system}

\end{enumerate}

\let\cleardoublepage\clearpage


\chapter{System Usability Interview} \label{appendix:interview}


\printtblhdr

\begin{enumerate}
\prop{I could find the certain course created by tutor.}

\prop{The process of asking a question or answering a question was simple.}

\prop{Voting score would help to locate the useful contribution.}

\prop{Integrated text input in the drawing tool would helps express the textual content.}

\prop{The drawing tool provided enough elements ready to be drawn.}

\prop{Quoting and modifying on top of others\' contributions are useful.}

\prop{I found the history function(undo redo) of drawing tool was really necessary.}

\prop{Auto-ordering of answers was seamless and unconspicuous.}

\prop{I found the real-time feature was interactive.}

\prop{The real-time feature didn't cause distraction while viewing the answers.}

\end{enumerate}



\end{appendices}

