The following chapter gives an overview of state of the art. To achieve the high interactivity and responsiveness in the graphical discussion system, a lot of modern web technologies should be applied.

However, there are always plenty of alternatives for each technology which could differ from system to system. So it is important to investigate and analyse the existing solutions and capture an overview about different alternatives of technologies. It's is also vital to understand the benefit and drawback of the technologies used.

First of all, the general modern web technology and development workflow will be introduced, which goes through our whole development and has a great impact on the development efficiency. The next part describes the different graphical technologies on web, and which fits our system best. Then an overview of the real-time communication technologies is illustrated and evaluated.

\section{Modern Web Development}
\input{Content/03/ModernWebDev}
% Seperation of Frontend and Backend,
\section{Graphics on the Web}
\input{Content/03/Graphics} \label{graphics-section}
% Graphics technologies on the web
\section{Real-Time Communication}
\input{Content/03/RTC}
% Realtime technologies, comparation of techs
% \section{Front-end Technologies}
% \input{Content/03/Client}
% Tech stack: React, Babel, ES6, ...
% \section{Efficient Server Side}
% \input{Content/03/Server}
% Tech stack: Nodejs (Why Node, comparation), MongoDB(Why, comparaion), Express?


% \section{Summary}
