Usability testing refers to evaluating a product or service by testing it with representative users. In principle, during a usability test, participants  will evaluate the system with quantitive metrics. 

The goal of usability testing is to collect the quantitive data, analyse the result and issue the usability problems with tested system. 

\subsection{System Usability Scale}

The System Usability Scale (SUS) offers a "quick and dirty", but relative reliable approach for measuring the usability\cite{brooke1996sus}.  It contains a 10 item questionnaire with five rating options for participants; from \textit{strongly agree} to \textit{strongly disagree}.


In order to calculate the SUS score, score contributions from each item should be calculated once separately at first. Score contribution will range from 0 to 4. For items with odd number, the score contribution should minus 1. For item with even number, the contribution is 5 minus the score. The sum of all scores is multiplied by 2.5 to obtain the overall value of SUS, which has a range of 0 to 100.

\begin{equation}
\label{formular:SUS}
SUS_{sum} = 2.5 \times \left (  \sum_{ i=1}^{5} \left ( a_{2i-1} - 1 \right ) + \sum_{ i=1}^{5} \left ( 5 - a_{2i} \right ) \right ) 
\end{equation}


\begin{table}[!htbp]
\centering
\begin{tabularx}{\textwidth}{@{}lXXXXXl@{}}
\toprule
Item(No.)   & A  & B  & C  & D  & E          & Average Score        \\ \midrule
1               & 3  & 4  & 3  & 4  & 4          & 3.6                     \\
2               & 2  & 1  & 1  & 1  & 2          & 1.4                     \\
3               & 5  & 4  & 4  & 5  & 4          & 4.4                     \\
4               & 1  & 2  & 1  & 2  & 2          & 1.6                     \\
5               & 4  & 4  & 3  & 4  & 5          & 4                     \\
6               & 4  & 5  & 4  & 3  & 4          & 4                     \\
7               & 5  & 4  & 4  & 5  & 5          & 4.6                     \\
8               & 3  & 3  & 2  & 1  & 3          & 2.4                     \\
9               & 5  & 4  & 3  & 4  & 5          & 4.2                     \\
10              & 2  & 3  & 2  & 1  & 2          & 2                     \\ \bottomrule        
\end{tabularx}
\caption{Score of SUS table}
\label{table:score-sus}
\end{table}

For the SUS testing of Graphicuss system, 5 participants are involved in the interview with SUS questionnaire, which is listed in appendix \ref{appendix:sus}. Each participant gives his own score contribution for each item, and the average score of each item is calculated. Table \ref{table:score-sus} shows the result.

According to the formula \ref{formular:SUS}, the final sum SUS score of the system is \textbf{73.5}.

\cite{bangor2009determining} \cite{gackenheimer2015core}\cite{barron1998minimum}\cite{grunwald2005advances}\cite{ferraiolo2000scalable}\cite{fette2011websocket}\cite{geary2012core}\cite{richardson2008restful}\cite{pautasso2008restful}\cite{pimentel2012communicating}



\subsection{Interview based Usability Test}